Inferring Neural Networks from Imaging Using Partial Correlation and Sample Weighting.

### 2014-05-20 article.tex
Re-work table of content
First bg and issue

\begin{abstract}
This is the abstract for this article.
\end{abstract}
\begin{keywords}
List of keywords
\end{keywords}
\cite{*}
\section{Introduction}
\label{sec:intro}
\section{Motivation \& objectives}
\section{Winning method}
\section{Results}
\section{Discussion on the evaluation metric}
\section{Comparison with other methods}

\bibliography{jmlr-sample}

\appendix

\section{First Appendix}\label{apd:first}

This is the first appendix.

>>>>

\begin{abstract}
This is the abstract for this article.
\end{abstract}

\begin{keywords}
List of keywords
\end{keywords}

\section{Introduction}\label{sec:intro}

% BG : brain, complex organ

Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.
The human brain is a complex biological organ, which is formed by 100
billions of neurons with 7000 synaptic connections on average. Inferring the
neuron connectivity network through dissection would be an impossible
and daunting task.

% Issue : we have data, but need to have to infer the connectome
Cutting edge optical devices (TODO CITE) allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator. From those imaging signals, the following inverse problem
is set: inferring the network connectivity from the chemical signals.

\section{Method}

\section{Empirical experiments}
\subsection{Datasets}
\subsection{Metrics}
\subsection{Data filtering}
\subsection{Signal distribution}
\subsection{ROC AUC results}
\subsection{AUPRC}

\section{Conclusion}

\bibliography{references}
